\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control for Energy and Thermal Comfort Optimization in Building Energy Systems using Random Forests}

### 2018-01-18 paper/final/intro.tex
edit related work and intro

\textcolor[rgb]{0,0,1}{The key question now is: can we employ data-driven techniques to reduce the cost of modeling, and still exploit the benefits that MPC has to offer?
We therefore look for automatic data-driven approaches to control, that are also adaptive, scalable and interpretable.
We solve this problem by bridging the gap between Machine Learning and Predictive Control. In particular, in this paper, we present a method based on Random Forests.}

@@

\subsubsection{Physics-based modeling}
\label{SSS:physics-based}
\textcolor[rgb]{0,0,1}{We describe the physics-based approach based on an RC network outlined in \cite{Sturzenegger2016}.
The building is modeled as a bilinear system constructed from physical principles.
The modeling process consists of three steps:
\begin{enumerate}
	\item Building geometry and construction data are used together with first-principles to derive the following linear model for the building's thermal dynamics:
		\begin{equation}\label{E:RCZoneEq}
			\dot x(t) = A_x x(t) + B_q q(t).
		\end{equation}
		This model describes the behavior of the zone, wall, floor and ceiling temperatures.
		Walls, floors and ceilings are considered as divided into layers with different features. Therefore, each zone was described with an RC network model (see Figure 3-10 in \cite{SturzeneggerTR}), where the capacitances represent the states of the layers and the resistances represent the thermal resistance of the layers.
%		\begin{figure}[t]
%			\begin{center}
%				\includegraphics[width=0.6\textwidth]{figures/RC_net.eps}
%				\caption{RC model of a zone. $q$ represents the external heat fluxes}\label{F:RCnet}
%			\end{center}
%		\end{figure}
		The heat exchange between two adjacent layers, i.e. layer ``a" and layer ``b", is modeled to be proportional to the temperature difference of the two layers and the corresponding thermal resistance $R$ given by
		\begin{equation}\label{E:RCHeatExchange}
			\begin{aligned}
				&C_a\dot x_a = \frac{x_b(t) - x_a(t)}{R},\\
				&C_b\dot x_b =  \frac{x_a(t) - x_b(t)}{R},
			\end{aligned}
		\end{equation}
		where $C_a$ and $C_b$ are the heat capacitances of the layers. This is done for each layer of each zone, obtaining the compact representation given in \eqref{E:RCZoneEq}. The thermal parameters are derived from zones geometry and material properties.
	\item External heat fluxes, modeled as a bilinear model, affect the building directly as well as indirectly through zones:
		\begin{equation}\label{E:RCfluxes}
			q(t) = A_q x(t) + B_{q,u}u(t) + B_{q,d}d(t) + \sum_{i=1}^{n_u}{[\left(B_{q,du,i}d(t) + D_{q,xu,i}x(t)\right)u_i(t)]},
		\end{equation}
		where $u$ are the inputs and $d$ the disturbances of the system.
%		Equation \eqref{E:RCfluxes} comes from a series of 20 equations analyzed in Section 3.3.1.3 of the Technical Report \cite{SturzeneggerTR}, that we do not report here for the sake of simplicity. 
Equation \eqref{E:RCfluxes} for the heat flux is obtained by modeling
	\begin{enumerate}
		\item heat exchange associated with the building hull (except for windows), both conductive and radiative part,
		\item  heat flux to each thermally activated building system (TABS), i.e. pipes buried in the concrete slabs of the floors carrying hot/cold water,
		\item heat flux through the windows in three different parts: radiation due to elements directly in contact with the zone air, conduction through the window, and absorption of the solar radiation through the window,
		\item convection due to internal gains due to occupants, appliances and lighting, and
		\item the effects of the AHU.
	\end{enumerate}
	\item The resulting system \eqref{E:RCZoneEq} is discretized with sampling time of $15\ \mathrm{min}$.
	This model has approximately 300 states, which include temperature of the zones, walls and floors on the second floor.
	The outputs of the system are the zone temperatures.
	Since the performance of the state estimation, that is needed to compute the optimal control inputs using MPC depends on the number of states, an approximated model with fewer states is needed.
	To this aim, different averaged temperatures of the building facades (North, South, West, East) and the zones are considered, obtaining an approximated model with 35 states.
	This  approximate model is then considered ``suitable for MPC" (see Section 3.3.1.4 in \cite{SturzeneggerTR}). 
\end{enumerate}}

\textcolor[rgb]{0,0,1}{In summary, the approximate model has the following state, input and disturbance variables:
	\begin{itemize}
		\item 5 outputs: averaged room temperature for each group of zones (North, South, West, East, Center). The rooms are equipped with temperature sensors.
		\item 18 inputs: TABS heating heat flux, TABS cooling heat flux, averaged transmitted solar heat flux for each group of zones (North, South, West, East) that is estimated using blinds position measurements, air massflow through the energy recovering mode, air massflow bypassing the energy recovering mode, air massflow through the air cooler, AHU heat coil heat flux, lighting power for the offices for each group of zones (North, South, West, East), and radiator heat flux in the corner offices (North, South, West, East).
		\item 7 disturbances: internal gains in the offices and internal gains in non-office zones, which are predicted using a standard schedule, ambient temperature and solar radiation on facade (North, South, West, East) whose values were obtained through Kalman filtering using measurements from the weather station placed on the roof of the building. This filtering is needed to take into account the shadowing of the neighboring buildings.
	\end{itemize}
An EnergyPlus model is built for this system, and model parameters of matrices $A_x$, $B_q$, $A_q$, $B_{q,u}$, $B_{q,d}$, $B_{q,du,i}$, $D_{q,xu,i}$ are derived using geometry and materials data from the EnergyPlus model.
This was a choice of the authors; real geometry and materials data can also be used to estimate the model parameters, although not always available. 
For this particular building, 24 parameters are estimated/taken form a datasheet/computed for the considered zone model.
Although some of the parameters are in common between different zones, the others are found independently for each zone.
To derive the EnergyPlus model using the available measurements and to use the same control implemented in the building, the EnergyPlus model is coupled with MATLAB using BCVTB \cite{Wetter2015}.\textcolor[rgb]{1,0,0}{ ADD THIS IS ONLY FOR ONE FLOOR, AND THAT THE OTHER ARE ASSUMED TO BE EQUAL. THIS IS TO EMPHASIZE THE COMPLEXITY}}
%To identify the model a total of 294 MATLAB signals were sent to the EnergyPlus model and a total of 1081 EnergyPlus signals were sent back to Matlab.

\textcolor[rgb]{0,0,1}{The physics-based approach, although detailed and accurate (in some cases), is cost and time prohibitive. The long and complex modeling procedure that is unique to every building poses a challenge in applying MPC to large scale buildings.}

@@

\textcolor[rgb]{0,0,1}{The goal with the data-driven modeling is to learn a function map
\begin{equation}
y(t) = f(u(t),\dots,u(t-\delta_u), d(t),\dots, d(t-\delta_d)),
\end{equation}
where \(y\) represents the outputs, \(u\) the inputs and \(d\) the disturbances as defined earlier, and \(\delta\) is a lag variable. If \(y\) is the average room temperature for one of the zones, a nonlinear function \(f\) is more appropriate, for example \(f\) may belong to the class of Neural Networks or Random Forests.\textcolor[rgb]{1,0,0}{???????????????}}

@@

	\item \textcolor[rgb]{0,0,1}{\textbf{Linearity assumption:} 
	During physical modeling in \eqref{E:RCHeatExchange}, in order to keep the model simple, the heat exchange between layers is modeled with a linear behavior. 
	Hence all the nonlinearities were neglected.
	In the case of heat flux in \eqref{E:RCfluxes}, a linear model is not good enough to provide a good approximation. For this reason a bilinear model was considered.
	However, more complex nonlinearities have been neglected due to the already high complexity of the model \cite{Sturzenegger2016}. 
	In data-driven modeling, we can relax these linearity assumptions as nonlinear functions can be learned rather efficiently and accurately.\textcolor[rgb]{1,0,0}{IT IS NOT CLEAR THAT THE DD ALGORITHM TAKE CARE OF IT CREATING ITS INTERNAL STRUCTURE}
	\item \textbf{Other assumptions:} 
	Due to the high modeling complexity, physical modeling neglects different geometries and different materials of the floors assuming they are the same for each floor which is never true in reality.
	In many cases, the details of construction layout and equipments are not even available so many parameters have to be guessed.
	Data-driven modeling depends on the sensor data directly. 
	Hence, such assumptions never arise.}

@@

A vast amount of literature exists dealing with methodologies for several energy efficiency applications in buildings, i.e. Demand Response, peak power reduction, energy saving and thermal comfort, and others.
All this approaches can be mainly classified considering 2 main features:

@@

	\item the system's model considered:

@@

			\item the only use of simulation tools, such as EnergyPlus \cite{energyPlus} and TRNSYS \cite{trnsys2000}: \cite{Yin2016EB,Christantoni2016EB};

@@

			\item control, typically Predictive Control, other than a modeling part: \cite{Shakouri2017SCS,Yoon2014EB,Yin2016EB,Salakij2016EB,Li2016E,Hu2017AE}.

@@

These papers are summarize in Table \ref{T:RelatedWork}, where all differences are highlighted.
We also emphasized the case studies the results are applied to, and whether the authors used experimental data to simulate their algorithms.
Only in 3 cases the algorithms were tested on real systems (in the table: RI - Real Implementation).
We can see that, except for the last 6 cases, which we will discuss more in detail in the rest of this section, when model-based approaches or only tools are considered, then also control techiniques are applied.
While with the data-driven modeling approaches, only model identification is addressed.
This is because bridging data-driven models with control theory, especially with the predictive control, introduces several issues \cite{Hou2013}.
Dealing with this kind of problems attracted a lot of researcher's attention in the past years.
We consider 6 of such works (the last 6 papers of Table \ref{T:RelatedWork}) that are more related to the methodology presented in this paper.

@@

However, the strategy is not easily scalable to different types of plants and does not use optimization theory in the closed-loop scheme.

@@

Reinforcement Learning is a model-free methodology and for this reason represents an alternative approach, with pros and cons, to the MPC \cite{Ernst2009TSMC}.

@@

However, Neural Networks are a particular type of machine learning algorithm that provides complex nonlinear equations to describe the system's dynamics.
For example, \cite{Afram2017} considers a data-driven state model in the MPC closed-loop optimization.
More precisely, Artificial Neural Networks are exploited to create data-driven models to be used as plant simulator in closed-loop with a Supervisory Model Predictive Control.

@@

Unfortunately, since Neural Networks models are nonlinear, the MPC based on such models is nonlinear as well.
This means that a global optimal solution can not be provided. Furthermore, due to the high number of neurons that a Neural Network usually needs to provide good models, the nonlinear MPC problem can results into a quite complex optimization problem to be solved.
To overcome this complexity problem, we proposed regression trees-based approaches in \cite{Behl2016,Jain2017TCPS}.
However these approaches suffer of some drawbacks.
In this paper, we provide a new methodology based on random forests, that overcome the drawbacks of our previous works.
It provides robustness with respect to disturbance uncertainties and has extremely good performance when compared to other approaches (both optimal and rule-based).
In the sext section we emphasize the differences with our previous approaches.

@@

\textcolor[rgb]{0,0,1}{
\subsubsection{Previous work}\label{SSS:PreviousWork}
In the following, the differences with respect to our previous papers are illustrated.
\begin{itemize}
	\item In \cite{Behl2016} we used regression trees and ensemble methods algorithms to create data-driven models for buildings. 
	We then setup an MPC-like control problem using the regression trees-based model to be used in the Demand-Response problem.
	However, ensemble methods have not been considered in the control process, but they have been used for identification purposes only.
	Furthermore, the proposed models allowed to optimally control the system considering only one-step lookahead prediction.
	Hence, it was not possible to use such approach to control the system considering a prediction over an horizon of arbitrary length.
	\item This problem was addressed in \cite{Jain2017TCPS}, where the regression trees algorithm was modified to allow the tree to provide multiple-output.
	Each output of the tree was then setup to provide the prediction of the system's behavior over different steps of the predictive horizon.
	This allowed us to setup an MPC-like control problem considering an arbitrary horizon.
	However, in this paper only single regression trees were considered, while ensemble methods were not took into account.
	Modeling accuracy using single trees is strongly subject to the problems of data overfitting and high variance.
	Such approach has the advantage to be extremely simple from the complexity point of view, but its application range is limited to specific kind of systems.
	\item In this work, we extend preliminary results gave in the conference papers \cite{JainACC2017}, where a simplified version of this approach was compared with a model-based control approach on a trivial system, and \cite{JainCDC2017}, where a more complex model was considered, but without taking into account any experimental data or forecast inaccuracy.
	In particular, an alternative approach is proposed to improve the system's identification accuracy and robustness of the previous approaches.
	More precisely, instead of considering a single tree with multiple output, we consider multiple trees with single output.
	Each tree is used to provide the prediction of the system's behavior over different steps of the horizon.
	Furthermore, we extend this approach considering the random forests.
	With a small increase in complexity, we setup an MPC-like control problem with arbitrary horizon, that provides better results and improves control robustness with respect to our previous work.
\end{itemize}
}

>>>>

\textcolor[rgb]{0,0,1}{The key question now is: can we employ data-driven techniques to reduce the cost of modeling, and still exploit the benefits that MPC has to offer?
We therefore look for automatic data-driven approaches to control, that are also adaptive, scalable and interpretable.
We solve this problem by bridging Machine Learning and Predictive Control. In particular, in this paper, we present a method based on Random Forests which uses historical data for receding horizon control.}

\textcolor[rgb]{0,0,1}{
Next, we present an example to illustrate how data-driven modeling reduces the cost of modeling buildings. 
}

@@

\subsubsection{Physics-based modeling}
\label{SSS:physics-based}
\textcolor[rgb]{0,0,1}{We describe the physics-based approach based on an RC network outlined in \cite{Sturzenegger2016}.
The building is modeled as a bilinear system constructed from physical principles.
The modeling process consists of three steps:
\begin{enumerate}
	\item Building geometry and construction data are used together with first-principles to derive the following linear model for the building's thermal dynamics:
		\begin{equation}\label{E:RCZoneEq}
			\dot x(t) = A_x x(t) + B_q q(t).
		\end{equation}
		This model describes the behavior of the zone, wall, floor and ceiling temperatures.
		Walls, floors and ceilings are considered as divided into layers with different features. Therefore, each zone was described with an RC network model (see Figure 3-10 in \cite{SturzeneggerTR}), where the capacitances represent the states of the layers and the resistances represent the thermal resistance of the layers.
%		\begin{figure}[t]
%			\begin{center}
%				\includegraphics[width=0.6\textwidth]{figures/RC_net.eps}
%				\caption{RC model of a zone. $q$ represents the external heat fluxes}\label{F:RCnet}
%			\end{center}
%		\end{figure}
		The heat exchange between two adjacent layers, i.e. layer ``a" and layer ``b", is modeled to be proportional to the temperature difference of the two layers and the corresponding thermal resistance $R$ given by
		\begin{equation}\label{E:RCHeatExchange}
			\begin{aligned}
				&C_a\dot x_a = \frac{x_b(t) - x_a(t)}{R},\\
				&C_b\dot x_b =  \frac{x_a(t) - x_b(t)}{R},
			\end{aligned}
		\end{equation}
		where $C_a$ and $C_b$ are the heat capacitances of the layers. This is done for each layer of each zone, obtaining the compact representation given in \eqref{E:RCZoneEq}. The thermal parameters are derived from zones geometry and material properties.
	\item External heat fluxes, modeled as a bilinear model, affect the building directly as well as indirectly through zones:
		\begin{equation}\label{E:RCfluxes}
			q(t) = A_q x(t) + B_{q,u}u(t) + B_{q,d}d(t) + \sum_{i=1}^{n_u}{[\left(B_{q,du,i}d(t) + D_{q,xu,i}x(t)\right)u_i(t)]},
		\end{equation}
		where $u$ are the inputs and $d$ the disturbances of the system.
%		Equation \eqref{E:RCfluxes} comes from a series of 20 equations analyzed in Section 3.3.1.3 of the Technical Report \cite{SturzeneggerTR}, that we do not report here for the sake of simplicity. 
Equation \eqref{E:RCfluxes} for the heat flux is obtained by modeling
	\begin{enumerate}
		\item heat exchange associated with the building hull (except for windows), both conductive and radiative part,
		\item  heat flux to each thermally activated building system (TABS), i.e. pipes buried in the concrete slabs of the floors carrying hot/cold water,
		\item heat flux through the windows in three different parts: radiation due to elements directly in contact with the zone air, conduction through the window, and absorption of the solar radiation through the window,
		\item convection due to internal gains due to occupants, appliances and lighting, and
		\item the effects of the AHU.
	\end{enumerate}
	\item The resulting system \eqref{E:RCZoneEq} is discretized with a sampling time of $15\ \mathrm{min}$.
	This model has approximately 300 states that include temperature of the zones, walls and floors on the second floor.
	The outputs of the system are the zone temperatures.
	Since the performance of the state estimation, that is needed to compute the optimal control inputs using MPC depends on the number of states, an approximated model with fewer states is needed.
	To this aim, different averaged temperatures of the building facades (North, South, West, East) and the zones are considered, obtaining an approximated model with 35 states.
	This  approximate model is then considered ``suitable for MPC" (see Section 3.3.1.4 in \cite{SturzeneggerTR}). 
\end{enumerate}}

\textcolor[rgb]{0,0,1}{In summary, the approximate model has the following state, input and disturbance variables:
	\begin{itemize}
		\item 5 outputs: averaged room temperature for each group of zones (North, South, West, East, Center). The rooms are equipped with temperature sensors.
		\item 18 inputs: TABS heating heat flux, TABS cooling heat flux, averaged transmitted solar heat flux for each group of zones (North, South, West, East) that is estimated using blinds position measurements, air massflow through the energy recovering mode, air massflow bypassing the energy recovering mode, air massflow through the air cooler, AHU heat coil heat flux, lighting power for the offices for each group of zones (North, South, West, East), and radiator heat flux in the corner offices (North, South, West, East).
		\item 7 disturbances: internal gains in the offices and internal gains in non-office zones, which are predicted using a standard schedule, ambient temperature and solar radiation on facade (North, South, West, East) whose values were obtained through Kalman filtering using measurements from the weather station placed on the roof of the building. This filtering is needed to take into account the shadowing of the neighboring buildings.
	\end{itemize}
An EnergyPlus model is built for this system, and model parameters of matrices $A_x$, $B_q$, $A_q$, $B_{q,u}$, $B_{q,d}$, $B_{q,du,i}$, $D_{q,xu,i}$ in Equations \eqref{E:RCZoneEq} and \eqref{E:RCHeatExchange} are derived using geometry and materials data from the EnergyPlus model.
This was a choice of the authors; real geometry and materials data can also be used to estimate the model parameters, if necessary data are available. 
For this particular building, 24 parameters are estimated/taken form a datasheet/computed for the considered zone model.
Although some of the parameters are in common between different zones, the others are found independently for each zone.
To simplify, the parameters of all the other floors are assumed to be identical which is not true in reality.
To derive the EnergyPlus model using the available measurements and to use the same control implemented in the building, the EnergyPlus model is coupled with MATLAB using BCVTB \cite{Wetter2015}.
}
%To identify the model a total of 294 MATLAB signals were sent to the EnergyPlus model and a total of 1081 EnergyPlus signals were sent back to Matlab.

\textcolor[rgb]{0,0,1}{The physics-based approach, although detailed and accurate (in some cases), is cost and time prohibitive. The long and complex modeling procedure that is unique to every building poses practical challenges in applying MPC to large scale buildings.}

@@

\textcolor[rgb]{0,0,1}{The goal with the data-driven modeling is to learn a function map
\begin{equation}
\label{E:MLexample}
y(t) = f(u(t),\dots,u(t-\delta_u), d(t),\dots, d(t-\delta_d)),
\end{equation}
where \(y\) represents the outputs, \(u\) the inputs and \(d\) the disturbances as defined earlier, and \(\delta\) is a lag variable.}

@@

	\item \textcolor[rgb]{0,0,1}{\textbf{Linearity assumption:}
	If \(y\) in Equation \eqref{E:MLexample} is the average room temperature for one of the zones, a nonlinear function \(f\) is more appropriate, for example \(f\) may belong to the class of Neural Networks or Random Forests. 
	During physical modeling in \eqref{E:RCHeatExchange}, in order to keep the model simple, the heat exchange between layers is modeled with a linear behavior. 
	Hence all the nonlinearities were neglected.
	In the case of heat flux in \eqref{E:RCfluxes}, again, a linear model is not good enough to provide a good approximation. For this reason a bilinear model was considered.
	However, more complex nonlinearities have been neglected due to the already high complexity of the model \cite{Sturzenegger2016}. 
	In data-driven modeling, we can relax these linearity assumptions as nonlinear functions can be learned rather efficiently and accurately.\textcolor[rgb]{1,0,0}{IT IS NOT CLEAR THAT THE DD ALGORITHM TAKE CARE OF IT CREATING ITS INTERNAL STRUCTURE}}

	\item \textcolor[rgb]{0,0,1}{\textbf{Other assumptions:} 
	Due to the high modeling complexity, physical modeling neglects different geometries and different materials of the floors assuming they are the same for each floor which is never true in reality.
	In many cases, the details of construction layout and equipments are not even available so many parameters have to be guessed.
	Data-driven modeling depends on the sensor data directly. 
	Hence, such assumptions never arise.}

@@

A vast literature exists in building energy applications that deals with Demand Response, peak power reduction, energy saving, thermal comfort, and related topics.
All these approaches can be classified based on two characteristics:

@@

	\item the type of system model:

@@

			\item simulation tool-based, such as EnergyPlus \cite{energyPlus} and TRNSYS \cite{trnsys2000}: \cite{Yin2016EB,Christantoni2016EB};

@@

			\item model identification and control (typically Predictive Control): \cite{Shakouri2017SCS,Yoon2014EB,Yin2016EB,Salakij2016EB,Li2016E,Hu2017AE}.

@@

These papers are summarizes in Table \ref{T:RelatedWork} highlighting the differences.
We also emphasize the case studies the results are applied to, and whether the authors use experimental data to simulate their algorithms.
Only in three cases the algorithms are tested on real systems (see Table: RI - Real Implementation).
We observe that except for the last 6 cases, which we discuss in detail, either model-based approaches or only tools are considered with/without control or data-driven modeling approaches without control.
%This is because bridging data-driven models with control theory, especially with the predictive control, introduces several issues \cite{Hou2013}.
Data-driven control has attracted increasing attraction in the recent years.
The last six papers of Table \ref{T:RelatedWork} that are more related to the methodology presented in this paper.

@@

However, the approach is not easily scalable to different types of plants and does not use optimization in the closed-loop scheme.

@@

Reinforcement Learning is a model-free methodology and is an alternative approach to MPC \cite{Ernst2009TSMC} (with pros and cons).

@@

%However, Neural Networks are a particular type of machine learning algorithm that provides complex nonlinear equations to describe the system's dynamics.
\cite{Afram2017} uses a Neural Network based data-driven state model as a plant simulator in the MPC closed-loop optimization.

@@

Unfortunately, since Neural Networks models are nonlinear, the MPC based on such models is also nonlinear.
This means that a global optimal solution can not be guaranteed. 
When the complexity of network is high, solving the optimization problem becomes harder due to nonlinearties.
To overcome this complexity, we introduced regression trees-based approach in \cite{Behl2016,Jain2017TCPS}.
In this paper, we provide a new methodology based on random forests, that overcome the drawbacks of our previous work.
It provides robustness with respect to disturbance uncertainties and has better performance when compared to other approaches (both optimal and rule-based).
In the next section, we emphasize the differences with our previous approaches.

@@

\textcolor[rgb]{0,0,1}{
\subsubsection{Previous work}\label{SSS:PreviousWork}
We highlight the differences with respect to our previous work.
\begin{itemize}
	\item In \cite{Behl2016} we use regression trees to setup an MPC problem and apply it to the problem of Demand-Response.
	However, these models can be used for optimal control with only one-step lookahead prediction.
	Hence, it is not possible to use such approach to control the system considering a prediction over an horizon of arbitrary length.
	\item This limitation is addressed in \cite{Jain2017TCPS}, where multi-output regression trees are used instead of single output trees.
	The different outputs correspond to different steps of the prediction horizon.
	This allows us to setup an MPC problem with a finite horizon.
	Modeling accuracy using single trees is strongly affected by overfitting and high variance.
	Such approach has the advantage to be extremely simple from the complexity point of view, but the range of applications is limited.
	\item In \cite{JainACC2017,JainCDC2017}, we take a different approach that improves the system's identification accuracy and robustness in MPC.
	Instead of considering a single tree/forest with multiple output, we consider multiple trees/forests with single output.
	Each tree/forest provides the prediction of the system's behavior for a different time step of the horizon.
	However, the results are based on simulated data and we did not account for inaccuracies in the weather forecast.
\end{itemize}
}
